\section{Analytics}
As we have previously mentioned, in our visualization plays a fundamental role the interactions between the available charts. In fact, the interactions transform a static visualization in a dynamic one, that is what we humans are used to seeing. For space reasons, we will represent with a $*$ all available charts in our project. In particular, the interactions provided are the following :
\begin{itemize}
\item \textbf{geographic map} $\rightarrow *$ : there is a possibility to select one or multiple battles through brushing technique. In particular, when a window is drawn, we can leverage its boundary in order to trigger a run time computation to exclude (i.e. hide them) the battles outside the brush and show only the ones inside it. At the end of this task, will be triggered another run time function that will update all the remaining charts, constraining their visualization domain in order to show only the selected battles.
\item \textbf{line chart} $\rightarrow$ \textbf{geographic map, stacked bar chart, scatter plot} : in this case we used brushing and zooming technique for a possible interaction. As before, with the brushing we are able to understand the subset of battles that we want to show and with zooming we are able to update axis's ranges and data. To make things clear, the zoom area is exactly the same of the brushing one. Once that this updates is performed, a run time function will be called to update the data shown in the geographic map, stacked bar chart and scatter plot.
\item \textbf{stacked bar chart} $\rightarrow$ null : this chart doesn't provide any interaction, it's only updated by others.
\item \textbf{box plot} $\rightarrow$ null : this chart doesn't provide any interaction, it's only updated by others.
\item \textbf{scatter plot} $\rightarrow$ \textbf{geographic map} : in this chart we have used the brushing approach to select a group of battles that will be highlighted with a dark border in case of light theme and with a white border in case of dark theme. This action will also trigger another run time function, which is responsible to highlight the selected battles also in the geographic map. 
\end{itemize}